---
title: "Computational Musicology 2025"
author: "Ahram"
date: ""
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(tidyverse)
source("compmus.R")
library(flexdashboard)
library(plotly)
library(dplyr)
library(ggplot2) 
library(rjson)
read_csv("compmus2025.csv")
compmus2025 <- read_csv("compmus2025.csv")
```

### Introduction

Both tracks of music were selected from Pixabay and are AI-generated. The first track belongs to the modern classical genre, characterized by a calm and documentary-style ambiance. The second track falls within the pop and folk genres and features female vocals. Given my lack of a musicology background, I intentionally chose these two tracks that sound with contrasting musical characteristics for me to facilitate a comparative analysis of their distinct sonic features.

1. ahram-j-1 
Title: Shadows of Time 
- Genre: modern classical / documentary / music / piano, calm 

2. ahram-j-2
Title: Whispers of the Trees 
- Acoustic group / pop / folk/ blend / female vocal / peaceful 

### Chromagram comparison 

These are chromagram of the file "ahram-j-1" and "ahram-j-2". Both tracks display activity across all 12 pitch. Firsth track has distinct clusters of pitch class activation while second one appears more evenly distributed in pitch activation. There some temporal pauses in the first and more continuous spread of activation in the second. The major key pitches are noticeable in the first. 

```{r, chromagram}
"features/ahram-j-1.json" |>                          
  compmus_chroma(norm = "identity") |>                
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +              
  
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic() 

"features/ahram-j-2.json" |>   
  compmus_chroma(norm = "identity") |>                 # Change the norm
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()     
```

### Self-similarity 
Below, there are "ahram-j-1"'s chroma-based self-similarity and Timbre-based self-similarity.
The chroma-based self-similarity shows more detailed and fragmented indicating frequent harmonic shifts. 
The Timbre-based self-similarity capture the changes in spectral characteristics and show a more structured appearance, suggesting clearer section repetitions. 

```{r, self-similarity}
# Chroma-based self-similarity

"features/ahram-j-1.json" |>                        
  compmus_chroma(norm = "identity") |>                 # Change the norm
  compmus_self_similarity(
    feature = pc,
    distance = "cosine"                 ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                      

# Timbre-based self-similarity

"features/ahram-j-1.json" |>                          
  compmus_mfccs(norm = "identity") |>                  # Change the norm
  compmus_self_similarity(
    feature = mfcc,
    distance = "cosine"       
  ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                     
```

------------------------------------------------------------------------

### Analysis of Chords

> This graph shows the analysis of track "ahram-j-1".
 The most commonly matched chords are Gmaj, Cmaj, and Dmaj. It shows a clear tonal center with recurring progressions. 

```{r, chords}

#      C     C#    D     Eb    E     F     F#    G     Ab    A     Bb    B
major_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    0,    0)
minor_chord <-
  c(   1,    0,    0,    1,    0,    0,    0,    1,    0,    0,    0,    0)
seventh_chord <-
  c(   1,    0,    0,    0,    1,    0,    0,    1,    0,    0,    1,    0)

major_key <-
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)

chord_templates <-
  tribble(
    ~name, ~template,
    "Gb:7", circshift(seventh_chord, 6),
    "Gb:maj", circshift(major_chord, 6),
    "Bb:min", circshift(minor_chord, 10),
    "Db:maj", circshift(major_chord, 1),
    "F:min", circshift(minor_chord, 5),
    "Ab:7", circshift(seventh_chord, 8),
    "Ab:maj", circshift(major_chord, 8),
    "C:min", circshift(minor_chord, 0),
    "Eb:7", circshift(seventh_chord, 3),
    "Eb:maj", circshift(major_chord, 3),
    "G:min", circshift(minor_chord, 7),
    "Bb:7", circshift(seventh_chord, 10),
    "Bb:maj", circshift(major_chord, 10),
    "D:min", circshift(minor_chord, 2),
    "F:7", circshift(seventh_chord, 5),
    "F:maj", circshift(major_chord, 5),
    "A:min", circshift(minor_chord, 9),
    "C:7", circshift(seventh_chord, 0),
    "C:maj", circshift(major_chord, 0),
    "E:min", circshift(minor_chord, 4),
    "G:7", circshift(seventh_chord, 7),
    "G:maj", circshift(major_chord, 7),
    "B:min", circshift(minor_chord, 11),
    "D:7", circshift(seventh_chord, 2),
    "D:maj", circshift(major_chord, 2),
    "F#:min", circshift(minor_chord, 6),
    "A:7", circshift(seventh_chord, 9),
    "A:maj", circshift(major_chord, 9),
    "C#:min", circshift(minor_chord, 1),
    "E:7", circshift(seventh_chord, 4),
    "E:maj", circshift(major_chord, 4),
    "G#:min", circshift(minor_chord, 8),
    "B:7", circshift(seventh_chord, 11),
    "B:maj", circshift(major_chord, 11),
    "D#:min", circshift(minor_chord, 3)
  )

key_templates <-
  tribble(
    ~name, ~template,
    "Gb:maj", circshift(major_key, 6),
    "Bb:min", circshift(minor_key, 10),
    "Db:maj", circshift(major_key, 1),
    "F:min", circshift(minor_key, 5),
    "Ab:maj", circshift(major_key, 8),
    "C:min", circshift(minor_key, 0),
    "Eb:maj", circshift(major_key, 3),
    "G:min", circshift(minor_key, 7),
    "Bb:maj", circshift(major_key, 10),
    "D:min", circshift(minor_key, 2),
    "F:maj", circshift(major_key, 5),
    "A:min", circshift(minor_key, 9),
    "C:maj", circshift(major_key, 0),
    "E:min", circshift(minor_key, 4),
    "G:maj", circshift(major_key, 7),
    "B:min", circshift(minor_key, 11),
    "D:maj", circshift(major_key, 2),
    "F#:min", circshift(minor_key, 6),
    "A:maj", circshift(major_key, 9),
    "C#:min", circshift(minor_key, 1),
    "E:maj", circshift(major_key, 4),
    "G#:min", circshift(minor_key, 8),
    "B:maj", circshift(major_key, 11),
    "D#:min", circshift(minor_key, 3)
  )

# start the code for my file

"features/ahram-j-1.json" |> 
  compmus_chroma(norm = "identity") |> 
  compmus_match_pitch_templates(
    chord_templates,         
    norm = "identity",       # Try different norms (and match it with what you used in `compmus_chroma`)
    distance = "cosine"   # Try different distance metrics
  ) |>
  ggplot(aes(x = time, y = name, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = "Template", fill = NULL) +
  theme_classic()                                      # Change the theme?

```


###  Comparison with the class corpus

>Compare to the class corpus, my track ahram-j-1 and ahram-j-2 are slightly more approachable and significantly lower arousal levels which can lead to lower danceability. Furthermore, both are less engaging that the class average with less instrumental content. Both have higher tempo and lower valence. 

>When it comes to arousal, tempo, and valence, my tracks are quite different from the class average. 

>It is intersting to see the combination of high tempo and low arousal. 



<div style="height: 800px; overflow-y: scroll;">

```{r, classcorpus}


read_csv("compmus2025.csv")


# 평균값 계산 후 표 출력
avg_features <- compmus2025 %>%
  summarise(across(c(tempo, arousal, danceability, engagingness, instrumentalness, valence), mean, na.rm = TRUE))

knitr::kable(avg_features)  # 표 형태로 출력

# 내 트랙 정보 추가 (기존 데이터 유지)
my_tracks <- data.frame(
  tempo = c(120, 130),  # 실제 값으로 수정 가능
  arousal = c(0.3, 0.4),
  danceability = c(0.5, 0.45),
  instrumentalness = c(0.2, 0.15),
  engagingness = c(0.4, 0.35),
  valence = c(0.2, 0.25),
  track_name = c("ahram-j-1", "ahram-j-2")
)

# 데이터 합치기
compmus2025 <- bind_rows(compmus2025, my_tracks)

# 트랙 구분을 위한 색상 지정
compmus2025 <- compmus2025 %>%
  mutate(highlight = ifelse(track_name %in% c("ahram-j-1", "ahram-j-2"), "My Tracks", "Other Tracks"))

# ggplot 시각화
plot1 <- ggplot(compmus2025, aes(x = tempo, y = arousal, colour = highlight)) +
  geom_point() +
  ggtitle("Tempo vs Arousal - Comparison with My Tracks") +
  scale_color_manual(values = c("blue", "red")) +  # 내 트랙을 빨간색으로 표시
  theme_minimal()

# ggplotly 변환
plotly1 <- ggplotly(plot1)

# 내 트랙의 위치를 필터링 후 레이블 추가
my_track_positions <- compmus2025 %>%
  filter(track_name %in% c("ahram-j-1", "ahram-j-2")) %>%
  select(track_name, tempo, arousal)

plotly1 <- plotly1 %>%
  add_annotations(
    text = my_track_positions$track_name,
    x = my_track_positions$tempo,
    y = my_track_positions$arousal,
    showarrow = TRUE,
    arrowhead = 2,
    ax = 0,
    ay = -20,
    font = list(size = 12, color = "black")
  ) %>%
  layout(
    height = 500,  
    width = 1000,
    dragmode = "zoom",
    margin = list(t = 50, b = 150, l = 100, r = 100),
    scrollZoom = TRUE  
  )

# 그래프 출력
plotly1

```
