---
title: "Computational Musicology 2025"
author: "Ahram"
date: ""
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(tidyverse)
source("compmus.R")
library(flexdashboard)
library(plotly)
library(dplyr)
library(ggplot2) 
library(rjson)
read_csv("compmus2025.csv")
compmus2025 <- read_csv("compmus2025.csv")
```

### Introduction

Both tracks of music were selected from Pixabay and are AI-generated. The first track belongs to the modern classical genre, characterized by a calm and documentary-style ambiance. The second track falls within the pop and folk genres and features female vocals. Given my lack of a musicology background, I intentionally chose these two tracks that sound with contrasting musical characteristics for me to facilitate a comparative analysis of their distinct sonic features.

### Visualisation

These are chromagram of the file "ahram-j-1" and "ahram-j-2"

```{r}
"features/ahram-j-1.json" |>                          
  compmus_chroma(norm = "identity") |>                
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +              
  
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic() 

"features/ahram-j-2.json" |>   
  compmus_chroma(norm = "identity") |>                 # Change the norm
  ggplot(aes(x = time, y = pc, fill = value)) + 
  geom_raster() +
  scale_y_continuous(
    breaks = 0:11,
    minor_breaks = NULL,
    labels = c(
                "C", "C#|Db", "D", "D#|Eb",
                "E", "F", "F#|Gb", "G",
                "G#|Ab", "A", "A#|Bb", "B"
              )
  ) +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()     
```

Below, there are "ahram-j-1"'s chroma-based self-similarity and Timbre-based self-similarity.

```{r}
# Chroma-based self-similarity

"features/ahram-j-1.json" |>                        
  compmus_chroma(norm = "identity") |>                 # Change the norm
  compmus_self_similarity(
    feature = pc,
    distance = "euclidean"                 ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                      

# Timbre-based self-similarity

"features/ahram-j-1.json" |>                          
  compmus_mfccs(norm = "identity") |>                  # Change the norm
  compmus_self_similarity(
    feature = mfcc,
    distance = "euclidean"       
  ) |>   
  ggplot(aes(x = xtime, y = ytime, fill = d)) + 
  geom_raster() +
  scale_fill_viridis_c(guide = "none") +               # Change the colours?
  labs(x = "Time (s)", y = NULL, fill = NULL) +
  theme_classic()                                     
```

------------------------------------------------------------------------

### Conclusion

```{r}


```
